HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
Added results table in data analysis
final speed data set
accuracy table
tasks & procedures

\section{Tasks and Procedures}

@@

>>>>

\section{Tasks and Procedures}
The experimenter explained the purpose of the experiment to the participant and answered any general questions about the experiment. Each participant completed the entry survey (Appendix D) and signed the consent form (Appendix C). The experimenter showed the participant the experimental setup and described the tasks. For the setup, the experimenter confirmed that all apps needed for testing are pre-installed on the phone and are currently open, and that both phones are plugged into a computer and are being monitored. The experimenter confirmed that the participant knew how to open the multitasking interface and use the copy and paste function on the phone.

Each participant performed 3 blocks of tasks twice, once on KitKat and then on Lollipop. There were 6 trials in total per participant. The order of trials was balanced such that each participant performed the same set of tasks in the same order, but starting on a different device. Half the participants were randomly chosen to start on KitKat first, while the other half started on Lollipop first. Each participant was handed a printed sheet outlining all the tasks (see Appendix A). The participant read each block of tasks and executed them in the order listed on the sheet. Each block was preceded by a setup session for the experimenter to setup the device  (see Appendix B). The participant completed the tasks at his/her own pace. At the commencement of the experiment (6 trials), the participant completed an exit survey (see Appendix E). The whole experiment took about 20 minutes to complete per participant.

@@

\begin{center}
 \begin{tabular}{|c c c|}
 \hline
 Participant Number & Kitkat Speed & Lollipop Speed \\ [0.5ex]
 \hline\hline
 1 & 2.52 & 2.19\\
 \hline
 2 & 2.46 & 2.59 \\
 \hline
 4 & 2.28 & 2.14 \\
 \hline
 5 & 2.80 & 3.27 \\
 \hline
 6 & 2.76 & 2.17 \\
 \hline
 7 & 1.96 & 1.89 \\
 \hline
 8 & 2.02 & 1.79 \\
 \hline
 9 & 2.60 & 2.67 \\
 \hline
 10 & 2.06 & 1.17 \\
 \hline
 11 & 2.95 & 1.87 \\
 \hline
 12 & 2.28 & 1.71 \\
 \hline
 13 & 2.88 & 1.85 \\
 \hline
 14 & 1.92 & 2.72 \\
 \hline
 15 & 2.05 & 2.46  \\
 \hline
 16 & 2.69 & 3.03 \\
 \hline
  17 & 1.73 & 2.00 \\
 \hline \hline
 Avg & 2.37 & 2.22 \\

 \hline
\end{tabular}
\end{center}

\begin{center}
$(F_{1, 15} = 1.19, ns )$
\end{center}

\begin{center}
 \begin{tabular}{|c c c|}
 \hline
 Participant Number & Kitkat Errors & Lollipop Errors \\ [0.5ex]
 \hline\hline
 1 & 1 & 1\\
 \hline
 2 & 10 & 5\\
 \hline
 4 & 0 & 0 \\
 \hline
 5 & 1 & 3 \\
 \hline
 6 & 4 & 1 \\
 \hline
 7 & 0 & 2 \\
 \hline
 8 & 0 & 1 \\
 \hline
 9 & 10 & 4 \\
 \hline
 10 & 1 & 0 \\
 \hline
 11 & 2 & 2 \\
 \hline
 12 & 3 & 3 \\
 \hline
 13 & 1 & 1 \\
 \hline
 14 & 0 & 0 \\
 \hline
 15 & 1 & 0  \\
 \hline
 16 & 2 & 1 \\
 \hline
  17 & 2 & 1 \\
 \hline \hline
 Avg & 2.37 & 1.56 \\

 \hline
\end{tabular}
\end{center}

\begin{center}
$(F_{1, 15} = 2.19, ns )$
\end{center}
